---
title: "tolerance curves plotting"
author: "Silas Tittes"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document: default
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
---

```{r setup}
#knitr::opts_knit$set(
#  root.dir = '~/Documents/Projects/tolerance-curve2/'
#  )
knitr::opts_knit$set(root.dir = normalizePath("..")) 
```

sim_params3
## Data prep
```{r}
source("load_data.R")
#draws <- read_csv("bayes/stan_par1_df.csv") #draws for penalized zero model
#draw_fits <- read_csv("bayes/tidy_curves.csv")


```


```{r}


# spp <- unique(emery$species) %>% sample(size = 1)
# d_em <- filter(emery, species == spp)
# c_draws <- sample(x = 1:ndraws, 100)
# c_draws <- 1
# 
# 
# test <- predictions(spp = spp, par_df = draws, x_draws = c_draws, p = c(0.95, 0.5))
# plot(test$l95$x, test$l95$upper, type = "n", ylim = c(0, max(test$l95$upper)))
# lines(test$l95$x, test$l95$upper)
# lines(test$l95$x, test$l95$lower)
# 
# polygon(c(test$l50$x,rev(test$l50$x)), 
#         c(test$l50$upper, rev(test$l50$lower)), 
#         col = "dodgerblue", border = F)
# lines(test$l50$x, test$l50$mu, col = "black", lwd = 3)
# points(d_em$treat, d_em$Inflor_biomass)

```


## Trace plots and stan summary
```{r}
#note parameters as discussed in paper are:
#a = alpha
#b = beta
#c = zeta
#d = delta
#e1 = epsilon
#traceplot for parameter for each species


stan_sum <- summary(
  stanDat, 
  par = c("shape1", "shape2", "stretch", "x_min", "x_max", "nu")
)$summary

options(xtable.sanitize.colnames.function=identity,
        xtable.sanitize.rownames.function=identity)
print.xtable(
  xtable(round(stan_sum, 2)), comment = F, file = "derived_files/stan_table.tex",
  tabular.environment='longtable', include.colnames = TRUE,
  floating=FALSE, add.to.row = list(pos = list(0), command = "\\hline \\endhead "))

pdf("figures/trace_a.pdf")
rstan::traceplot(stanDat, par=c("shape1"))
dev.off()

pdf("figures/trace_b.pdf")
rstan::traceplot(stanDat, par=c("shape2"))
dev.off()

pdf("figures/trace_c.pdf")
rstan::traceplot(stanDat, par=c("stretch"))
dev.off()

pdf("figures/trace_d.pdf")
rstan::traceplot(stanDat, par=c("x_min"))
dev.off()

pdf("figures/trace_e.pdf")
rstan::traceplot(stanDat, par=c("x_max"))
dev.off()

# pdf("figures/trace_beta_0.pdf")
# rstan::traceplot(stanDat, par=c("beta_0"))
# dev.off()
# 
# pdf("figures/trace_beta_1.pdf")
# rstan::traceplot(stanDat, par=c("beta_1"))
# dev.off()

pdf("figures/trace_nu.pdf")
rstan::traceplot(stanDat, par=c("nu"))
dev.off()

```


## Raw parameter prob differences
```{r}


gen_comp <- function(var, cut = 0.95){
  
  high <- cut
  low <- 1 - cut
  
  var_df <- draws %>%
    select(species, draw, one_of(var)) %>%
    rename_(var = var) %>%
    spread(key = species, value = var) %>%
    select(-draw)
  
  map_df(var_df, ~{
    map_dbl(var_df, function(x){
      comp_p <- mean(.x > x)
      ifelse(comp_p > high | comp_p < low, round(mean(.x - x), 2), NA)
    })
  }) %>% as.matrix
}

quant_diff <- function(var, cut = 0.95){
  comp_mat <- gen_comp(var)
  lower_mat <- comp_mat[lower.tri(comp_mat)]
  round(mean(!is.na(lower_mat)) * 100, 0)
  
}


xmax_comps <- gen_comp("x_min")
rownames(xmax_comps ) <- colnames(xmax_comps )

sum(xmax_comps["glaberrima",] < 0, na.rm = T)
xmax_comps[,"glaberrima"]


comp_matrices <- function(var, cut = 0.95){
  
  map_comp_p <- gen_comp(var)
  perc_diff <- quant_diff(var)
  
  map_comp_p[upper.tri(map_comp_p, diag = T)] <- NA
  map_comp_p <- cbind(colnames(map_comp_p), map_comp_p)
  colnames(map_comp_p) <- paste0(substr(colnames(map_comp_p), 1, 2), ".")
  colnames(map_comp_p)[1] <- tab_strings[which(post_params == var)]
  
  write.csv(map_comp_p, 
            file = paste0("derived_files/parameter_comp_matrices/",
                          var,
                          "_matrix.csv")
  )
  
  cap <- str_glue("Pairwise comparisons among taxa for parameter, {var} ({perc_diff}\\% differ)") %>%
    gsub(pattern = "_", replacement = "\\\\_") %>%
    as.character()
  
  options(xtable.sanitize.colnames.function=identity,
          xtable.sanitize.rownames.function=identity)
  
  print.xtable(xtable(map_comp_p, caption = cap), 
               file = pair_file, 
               caption.placement = "top",
               append = TRUE, 
               include.rownames=FALSE)
  
}



post_params <- c("x_min", "maxima", "x_max", "stretch", "breadth", "area")
# tab_strings <- c("$\\delta$", "optima", "$\\epsilon$", "$\\zeta$", "$\\epsilon - \\delta$", "area")
tab_strings <- gsub(pattern = "_", replacement = "\\\\_", x = post_params) %>%
  gsub(pattern = "maxima", replacement = "optimum", x = .)
names(post_params) <- tab_strings 
pair_file <- "derived_files/parameter_comp_matrices/post_all_comparisons.tex"
file.create(pair_file)
post_params %>% map( ~ comp_matrices(var = .x)) %>% invisible

```



## concept plot of curves
```{r}

plot_concept <- function(){
  #conceptual plot over top of densities
  off <- 0.1
  a <- 4
  b <- 2.7
  c <- 5.5
  d <- 0
  e <- 1
  xseq_0 <- seq(0,1, length.out = 500)
  xseq_a <- xseq_0 * (e - d) + d
  fa = performance_mu(xseq_0, a, b, c, d, e)
  opt_loc <- (((a - 1)/(a*b - 1))^(1/a) * (e - d) + d)
  low_loc <- d
  high_loc <- e
  bredth <- e - d
  
  arr_len <- 0.05
  par_cex <- 1
  
  par(mar = c(3, 2, 1, 1)*1.1)
  plot(xseq_a, fa, type = "l", lwd = 2, axes = F, xlab = "", ylab = "",
       ylim = c(0, max(fa)*1.25) )
  axis(1, labels = F); axis(2, labels = F)
  mtext(text = "Fitness", side = 2, line = 1.2)
  mtext(text = "Environment", side = 1, line = 1.2)
  
  #polygon for area
  polygon(x = c(rev(xseq_a), xseq_a), y = c(rep(0, length(fa)), fa), 
          density = 100, col = alpha("black", 0.05), border = T, lwd = 2)
  text(0.7, mean(fa), "area*")
  
  text(x = opt_loc, y = max(fa)*(1-off), "optima*")
  points(x = opt_loc, y = max(fa), pch = 21, bg = "white", cex = 1.2)
  
  
  #text(x = low_loc, y = max(fa)*off, expression(delta), cex = par_cex)
  text(x = low_loc + 0.05, y = max(fa)*off, "x_min", cex = par_cex)
  points(x = low_loc, y = 0, pch = 21, bg = "white", cex = 1.2)
  
  #text(x = high_loc, y = max(fa)*off, expression(epsilon), cex = par_cex)
  text(x = high_loc - 0.1, y = max(fa)*off, "x_max", cex = par_cex)
  points(x = high_loc, y = 0, pch = 21, bg = "white", cex = 1.2)
  
  #segment for zeta
  #calc kums with zeta = 1
  z1 <- max(performance_mu(xseq_0, a, b, 1, 0 ,1))
  za <- max(fa)
  zeta_loc <- low_loc + 0.25
  arrows(x0 = zeta_loc, y0 = za, x1 = zeta_loc, y1 = z1, 
         code = 3, angle = 90, length = arr_len, lwd = 2, col = "grey50")
  #text(x = zeta_loc + 0.02, y = (z1+za)/2, expression(zeta), cex = par_cex)
  text(x = zeta_loc + 0.05, y = (z1+za)/2, "stretch", cex = par_cex)
  
  
  yy <- 4
  arrows(x0 = 0, y0 = max(fa)+1, x1 = high_loc, y1 = max(fa)+1, 
         code = 3, angle = 90, length = arr_len, lwd = 2, col = "grey50")
  
  #text(x = median(xseq_a), y = max(fa)+2.5, expression(epsilon - delta), cex = par_cex)
  text(x = median(xseq_a), y = max(fa)+2.5, "breadth*", cex = par_cex)
  
}

plot_concept()
```

## DAG

```{r}
plt_par <- function(input, coord, plot = F, rng = NULL, ...){
  if(plot){
    par(mar = c(0,0,1,0))
    plot(NA, NA, 
         xlim = c(rng[1], rng[2]), 
         ylim = c(rng[3], rng[4]), 
         axes = F, 
         xlab = "", 
         ylab = "")
  }
  input <- substitute(input)
  text(coord[1],coord[2], eval(expression(input)), ...)  
}


plot_dag <- function(){
  
  
  #l1_x <- c(0.8, 2, 3.75)
  l1_x <- c(0.8, 2)
  l2_x <- l1_x
  #l3_x <- c(1.2, 1.6, 2, 2.4, 2.8, 3.5, 4)
  l3_x <- c(1.2, 1.6, 2, 2.4, 2.8)
  l4_x <- c(0.8, l3_x)
  
  
  l1 <- 4
  l2 <- 3
  l3 <- 2
  l4 <- 1
  buff <- 0.15
  arl <- 0.05
  tpos <- 4
  xtpos <- 0.4
  rng <- c(0.5, max(l3_x) + 1.25, l4 - 0.1, l1 + 0.1)
  
  plt_par(x[ij], 
          coord = c(l1_x[1], l1), 
          plot = T, 
          rng = rng)
  
  #text(2, 4.5, "( Reproductive biomass )")
  #abline(v = 3.15, lty = 3, col = "grey")
  #text(3.75, 4.5, "( Mortality )")
  
  #level 1  
  plt_par(y[ij], coord = c(l1_x[2], l1))
  plt_par(z[ij], coord = c(l1_x[3], l1))
  
  #x to y
  arrows(l1_x[1] + buff, l1, l1_x[2] - buff, l1, length = arl, lty = 2)
  #arrows(l1_x[3] - buff, l1, l1_x[2] + buff, l1, length = arl)
  
  
  
  #level 2
  plt_par(mu[ij], coord = c(l2_x[2], l2), col = "blue")
  plt_par(p[ij], coord = c(l2_x[3], l2), col = "blue")
  
  #mu to y
  arrows(l2_x[2], l2+buff, l2_x[2], l1-buff, length = arl)
  
  #mu to p
  arrows(l2_x[2]+buff, l2, l2_x[3]-buff, l2, length = arl)
  
  #p to z
  arrows(l2_x[3], l2+buff, l2_x[3], l1-buff, length = arl)
  
  #p to y
  arrows(l2_x[3]-buff, l2+buff, l2_x[2]+buff, l1-buff, length = arl)
  
  
  #level 3
  plt_par(nu[j], coord = c(l4_x[1], l3))
  
  plt_par(shape1[j], coord = c(l3_x[1], l3))
  plt_par(shape2[j], coord = c(l3_x[2], l3))
  plt_par(stretch[j], coord = c(l3_x[3], l3))
  plt_par(x_min[j], coord = c(l3_x[4], l3))
  plt_par(x_max[j], coord = c(l3_x[5], l3))
  
  
  #nu to y
  arrows(l4_x[1], l3+buff, l2_x[2]-buff, l1-buff, length = arl)
  
  #a,b,c,d,e to mu
  for(i in 1:5){
    arrows(l3_x[i], l3+buff, l2_x[2], l2-2*buff, length = 0)
  }
  
  #connector to mu
  arrows(l2_x[2], l2-2*buff, l2_x[2], l2-buff, length = arl)
  
  
  plt_par(beta[0[j]], coord = c(l3_x[6], l3), cex = 1)
  plt_par(beta[1[j]], coord = c(l3_x[7], l3), cex = 1)
  
  #beta_0 to p
  arrows(l3_x[6], l3+buff, l2_x[3], l2-2*buff, length = 0)
  
  #beta_1 to p
  arrows(l3_x[7], l3+buff, l2_x[3], l2-2*buff, length = 0)
  
  #connector to p
  arrows(l2_x[3], l2-2*buff, l2_x[3], l2-buff, length = arl)
  
  #level4
  plt_par(gamma[nu], coord = c(l4_x[1], l4))
  plt_par(gamma[shape1], coord = c(l4_x[2], l4))
  plt_par(gamma[shape2], coord = c(l4_x[3], l4))
  plt_par(gamma[stretch], coord = c(l4_x[4], l4))
  plt_par(gamma[x_min], coord = c(l4_x[5], l4))
  plt_par(gamma[x_max], coord = c(l4_x[6], l4))
  
  plt_par(mu[beta[0]], coord = c(l4_x[7], l4), cex = 1)
  plt_par(mu[beta[1]], coord = c(l4_x[8], l4), cex = 1)
  
  
  #nu to nu
  arrows(l4_x[1], l4 + buff, l4_x[1], l3 - buff, length = arl)
  
  #abcdeb0b1 to abcdeb0b1
  for(i in 2:8){
    arrows(l4_x[i], l4 + buff, l3_x[i-1], l3 - buff, length = arl)  
  }
  
  #info text
  abline(v = max(l3_x) + xtpos, col = "grey")
  text(max(l3_x) + xtpos, l1, "Data", pos = tpos)
  text(max(l3_x) + xtpos, l2, "Computed", pos = tpos)
  text(max(l3_x) + xtpos, l3, "Species level", pos = tpos)
  text(max(l3_x) + xtpos, l4, "Group level", pos = tpos)
  
  
}

plot_dag()
```


## New concept fig
```{r}
cairo_pdf(filename = "figures/fig2_new.pdf")
par(mfrow = c(2,1))
plot_dag()
plot_concept()
dev.off()
```


## Reviewer suggested alternative to figure 3 (error bars)
```{r}
source("derived_files/state_reg.R")
grad_df <- gen_gradient_df(tolerance_df = draws)


q_low <- function(x) quantile(x, probs = 0.225, na.rm = T)
q_hi <- function(x) quantile(x, probs = 0.975, na.rm = T)


err_df <- grad_df %>%
  select(species, shape1, shape2, stretch, x_min, x_max, maxima, Mean, SE) %>%
  group_by(species) %>%
  summarise_all(.funs = list(mean = mean, `5th` = q_low, `95th` = q_hi)) %>%
  ungroup() %>%
  mutate(mpse = Mean_mean + SE_mean,
         mmse = Mean_mean - SE_mean) %>%
  left_join(., select(grad_df, species, aqua_terr2terr) %>% unique(), by = "species") %>%
  mutate(species = factor(species, levels = lasth$tip.label[lasth$edge[,2][lasth$edge[,2] <= length(lasth$tip.label)]]))


plot_err <- function(df = err_df, var, var_lo, var_hi, param, first = F, standard = T){
  
  if(standard){
    meen <- paste0(enquo(var), "_mean")
    lo <- paste0(enquo(var), "_5th")
    hi <- paste0(enquo(var), "_95th")
    par_plot_df <- df %>%
      select(species, !! meen[2], !! lo[2], !! hi[2], aqua_terr2terr) %>%
      rename(var_mean = !! meen[2],
             var_lo = !! lo[2],
             var_hi = !! hi[2])
  } else {
    meen <- enquo(var)
    lo <- enquo(var_lo)
    hi <- enquo(var_hi)
    par_plot_df <- df %>%
      select(species, !! meen, !! lo, !! hi, aqua_terr2terr) %>%
      rename(var_mean = !! meen,
             var_lo = !! lo,
             var_hi = !! hi)
  }
  
  par_plot <- par_plot_df %>% 
    ggplot(aes(var_mean, species, colour = aqua_terr2terr)) +
    geom_errorbarh(height = 0.25, colour = "black", aes(xmin=var_lo, xmax=var_hi), inherit.aes = T) +
    geom_point(alpha = 0.9) +
    xlab(param) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 4)) +
    scale_colour_manual(values=topo.colors(n = 12, alpha = 1)[c(11,4)]) +
    theme_minimal() +
    theme(legend.position = "none",
          panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank()) 
  
  if(first){
    par_plot
  } else{
    par_plot  + 
      theme(axis.title.y=element_blank(),
            axis.text.y=element_blank(),
            axis.ticks.y=element_blank(),
            axis.line.y=element_blank())
    
    
  }
  
}

d <- plot_err(var = x_min, param = "x_min", first = T) +
  theme(axis.text.y=element_text(face="italic"))
maxi <- plot_err(var = maxima, param = "optimum") 
e <- plot_err(var = x_max, param = "x_max") 
c <- plot_err(var = stretch, param = "stretch")


miss <- err_df %>%
  filter(is.na(Mean_mean)) %>%
  mutate(mmse = 0.08,
         mpse = max(err_df$mpse, na.rm = T))
  
se <- plot_err(var = Mean_mean, var_lo = mmse, var_hi = mpse, param = "depth (cm)", standard = F) +
  geom_segment(data = miss, 
               aes(mmse, species, xend = mpse, yend = species),
               inherit.aes = F,
               colour = "grey30",
               arrow = arrow(length = unit(0.12, "cm"))) +
  theme(panel.border = element_rect(colour = alpha("black", 0.5), fill=NA, size=0.5))
  

cairo_pdf(filename = "figures/fig3.pdf", width = 9, height = 5)
d + maxi + e + c + se + plot_layout(nrow = 1)
dev.off()

```




## Parameter density plot with phylogeny version 2
```{r, eval=FALSE}

source("derived_files/state_reg.R")
#set habitat colors
colz <- topo.colors(n = 12, alpha = 0.7)[c(11,4)]
colz2 <- topo.colors(n = 12, alpha = 1)[c(11,4)]
names(colz) <- c("terrestrial","vernal")
colz_par <- colz[match(state_reg_aqua_terr2terr, names(colz))]
names(colz_par) <- names(state_reg_aqua_terr2terr)


spp_list <- rev(lasth$tip.label[lasth$edge[,2][lasth$edge[,2] <= length(lasth$tip.label)]])

#pdf("figures/fig3.pdf")
#png(filename = "figures/fig4_curves.png")

cnc <- 1
ml <- rbind(c(0, 0, 0, 0, 0, 0),
            c(0, 1, 1, 1, 0, 0),
            c(0, 1, 1, 1, 0, 0),
            c(0, 1, 1, 1, 0, 0),
            cbind(rep(2,length(spp_list)),
                  matrix(seq_along(spp_list)+1+cnc), 
                  matrix(seq_along(spp_list)+length(spp_list)+1+cnc),
                  matrix(seq_along(spp_list)+2*length(spp_list)+1+cnc),
                  matrix(seq_along(spp_list)+3*length(spp_list)+1+cnc),
                  matrix(seq_along(spp_list)+4*length(spp_list)+1+cnc)),
            rep(0, 6), rep(0, 6))

layout(ml)

par(mar = c(2,2,0,0))
plot_concept()
par(mar = c(0,0,0,0))

plot.phylo(lasth, edge.width = 2, show.tip.label = F)

post_params <- c("x_min", "maxima", "x_max", "stretch")
greek_params <- c(expression(delta), expression(optima), expression(epsilon), expression(zeta))


seq_along(post_params) %>% walk(function(x){
  var <- post_params[x]
  den_var <- draws %>% 
    group_by(species) %>%
    do(den = density(.[[var]]))
  
  den_range <- den_var$den %>% map_df(~{
    xl = quantile(.x$x, 0) 
    xh = quantile(.x$x, 1)
    # xl = quantile(.x$x, 0.025)
    # xh = quantile(.x$x, 0.975)
    yl = 0
    yh = quantile(.x$y, 1)
    cbind(xl, xh, yl, yh) %>% as_data_frame
  }) %>% summarise_all(funs(min, max))
  
  
  
  names(den_var$den) <- den_var$species
  
  seq_along(spp_list) %>% map(~{
    spp_den <- den_var$den[[spp_list[.x]]] 
    plot(spp_den$x, spp_den$y,
         xlim = c(den_range$xl_min, den_range$xh_max),
         ylim = c(0, den_range$yh_max),
         axes = F, type = "n")
    polygon(spp_den$x, spp_den$y, col = colz_par[spp_list[.x]], border  = T)
    
    #segments(x0 = , x1 = , y0 = 0, y1 = 0)
    
    if(var == "d") legend("left", spp_list[.x], bty = "n", cex = 0.8)
  })
  axis(1)
  mtext(greek_params[x], side = 1, line = 3)
})


select <- dplyr::select
rename <- dplyr::rename
gradient <- read.xls("data/Pool depths_FINAL summary_REVISED.xls", 
                     header = T, skip = 1, stringsAsFactors = F) %>%
  mutate(taxa = strsplit(X, "_") %>% map_chr(~ .x[length(.x)]),
         taxa = ifelse(taxa == "deblilis", "debilis", taxa)) %>% 
  filter(taxa %in% as.character(unique(emery$species)))


limz <- gradient %>%
  rowwise() %>%
  summarise(high = Mean + SE,
            low = Mean - SE) %>%
  summarise(maxy = max(high, na.rm = T)*1.1,
            miny = min(low, na.rm = T)*1.1)

spp_list %>%
  walk(~{
    row_i <- gradient %>% filter(taxa == .x)
    par(mar = c(0,0,0,2))
    plot(
      NA, NA, 
      ylim =c(-0.1, 0.5),
      xlim = c(limz$miny, -limz$miny),
      axes = F, bty = "n")
    segments(
      y0 = 0,
      y1 = 0,
      x0 = row_i$Mean - row_i$SE, 
      x1 = row_i$Mean + row_i$SE,
      lwd = 1
    )
    points(row_i$Mean, 0, pch = 19)
    abline(v = 0, lty = 2)
    #text(0.3, limz$maxy, row_i$taxa)
    if(.x == spp_list[length(spp_list)]){
      axis(1, cex.axis = 0.85, 
           at = round(seq(limz$miny, -limz$miny, length.out = 4),2),
           labels = round(seq(limz$miny*100, -limz$miny*100, length.out = 4),0))
      mtext(side = 1, "depth (cm)", line = 3, cex = 0.85)              
    }
  })

#dev.off()

```






## curve plots
```{r}
#set habitat colors
source("derived_files/state_reg.R")
colz <- topo.colors(n = 12, alpha = 1)[c(11,4)]
colz2 <- topo.colors(n = 12, alpha = 1)[c(11,4)]
names(colz) <- c("terrestrial","vernal")
colz_par <- colz[match(state_reg_aqua_terr2terr, names(colz))]
names(colz_par) <- names(state_reg_aqua_terr2terr)

sppMaxVal <- by(data = emery$Inflor_biomass, 
                INDICES = emery$sppint, FUN = max)
names(sppMaxVal) <- unique(emery$species)


#plot data
spp_list <- rev(lasth$tip.label[lasth$edge[,2][lasth$edge[,2] <= length(lasth$tip.label)]])

#pdf(paste0(getwd(),"/figures/tree_tolerance.pdf"))
#png(filename = "figures/fig3_tree_tolerance.png") #alt


pdf("figures/fig2.pdf") #alt
#svg("figures/fig3_tree_tolerance.svg") #alt

c1 <- rep(1, length(spp_list))
c_2_4 <- rep(0, length(spp_list))
c3 <- 2:(length(spp_list)+1)
m_lay <- cbind(c1, c1, c1, c3, c3, c_2_4)
m_lay <- rbind(rep(0, ncol(m_lay)), m_lay, rep(0, ncol(m_lay)))
layout(m_lay, 
       widths = c(0.25, 0.25, 0.25, 0.2, 0.2, 0.05), 
       heights = c(0.01, rep(1/(nrow(m_lay)-2), (nrow(m_lay)-2)), 0.05) )

par(mar=c(0,0,0,0))

plot.phylo(lasth, show.tip.label = F, edge.width = 4, 
           no.margin = T)
tiplabels(pch = 22, cex = 3,
          bg = colz[state_reg_aqua_terr2terr[lasth$tip.label]])

#format node support for labeling
node_fmt <- ifelse(lasth$node.label < 1, 
                   substring(sprintf("%4.2f", lasth$node.label), 2),
                   lasth$node.label)

nodelabels(node_fmt, frame = "n", 
           cex = 1, font = 2, pos=4, offset = 1)


legend("bottomleft", c("Terrestrial", "Vernal pool"), pch = 22, pt.cex = 1.5,
       pt.bg = colz, cex = 1.2, bg = "white")


set.seed(123)
n_draws <- sample(1:ndraws, 100)

xrng <- draws %>% 
  filter(draw %in% n_draws) %>%
  summarise(mnx = min(x_min),
            mxx = max(x_max))
xrng <- c(xrng$mnx, xrng$mxx)
yrng <- max(emery$Inflor_biomass)*1.25


for(spp in spp_list){
  
  #spp <- "glaberrima"
  subEm <- emery %>% filter(species == spp)
  spp_draws <- draws %>% filter(draw %in% n_draws, species == spp)
  
  x_seq = seq(min(spp_draws$x_min), 
              max(spp_draws$x_max), 
              length.out = 100)
  
  test <- predictions(x = x_seq, spp = spp, par_df = spp_draws, x_draws = n_draws, p = c(0.95, 0.5))
  
  
  mean_opt <- spp_draws %>%
    summarise(opt = mean(maxima)) %>%
    pull()
  mean_opt_df <- test$l95[which.min((test$l95$x - mean_opt)^2),]
  
  max_y <- max(max(test$l95$upper), max(subEm$Inflor_biomass))
  
  par(mar=c(0,2,0,2))
  #plot(NA, NA, ylim=c(-0.5, yrng), xlim = xrng, axes = F, xlab = "", ylab = "")
  plot(NA, NA, ylim=c(0, max_y*1.1), 
       xlim = xrng, axes = F, xlab = "", ylab = "")
  box()
  
  pos <- seq(max_y*0.2, max_y*0.8, length.out = 3)
  axis(side = 2, 
       cex.axis = 0.75, 
       at = pos, 
       labels = round(pos, 1),
       las = 1, 
       tck = -0.02,
       mgp=c(0, 0.2, 0)
  )
  
  
  polygon(c(test$l95$x,rev(test$l95$x)),
          c(test$l95$upper, rev(test$l95$lower)),
          col = alpha(colz[state_reg_aqua_terr2terr[spp]], 0.2),
          border = colz[state_reg_aqua_terr2terr[spp]],
          lwd = 0.25)
  
  polygon(c(test$l50$x,rev(test$l50$x)),
          c(test$l50$upper, rev(test$l50$lower)),
          col = colz[state_reg_aqua_terr2terr[spp]], 
          border = F)
  
  
  lines(test$l50$x, test$l50$mu, lwd = 1, col = "grey40")
  
  points( jitter(subEm$treat, factor = 0.2), subEm$Inflor_biomass,
          pch=19, cex = 0.5, col = alpha("black", 0.5))
  
  #points(mean_opt_df$x, mean_opt_df$mu, pch = "|", cex = 0.75, col = alpha("black", 0.5))
  abline(v = mean_opt, lty = 2, col = alpha("black", 0.5), lwd = 0.75)
  
  legend("topleft", spp, bty="n", text.font = 3)
}

#axis(side = 2, cex.axis = 0.85, las = 1, tck = -0.02, mgp=c(0, 0.2, 0))
axis(side = 1, cex.axis = 0.85, tck = -0.02, line = 0, mgp=c(0, 0.2, 0))
mtext(text = "hydrology treatment", side = 1, cex = 0.7, line = 1)
mtext(text = "reproductive biomass", side = 2, cex = 0.7, line = 1.5, adj = 0)

dev.off()

```


## Plotting observed versus predicted

```{r}

d_1 <- sample(1:ndraws, 1)
resid_df <- 1:nrow(emery) %>% map_df(~{
  em_row <- emery %>% slice(.x)
  draws %>% filter(species == em_row$species) %>%
    filter(draw %in% d_1) %>%
    group_by(draw) %>%
    do({
      nu <- .$nu
      performance_mu(em_row$treat, .$shape1, .$shape2, .$stretch, .$x_min, .$x_max) %>% 
        as_tibble() %>%
        rename(predicted = value) %>% 
        mutate(species = em_row$species,
               treat = em_row$treat,
               Inflor_biomass = em_row$Inflor_biomass,
               res = em_row$Inflor_biomass - predicted
        )
    }) %>%
    ungroup()
})


cairo_pdf("figures/figB11.pdf")
plot(resid_df$predicted, resid_df$res,
     xlab = "fitted values", ylab = "residuals")
lines(loess.smooth(resid_df$predicted, resid_df$res), lty = 1)
abline(h = 0, lty = 2, col = "blue")
dev.off()

# resid_df %>%
#   ggplot(aes(predicted, res)) +
#   geom_point() +
#   geom_smooth(se = F) +
#   theme_minimal()

# plot(resid_df$predicted, resid_df$res/(resid_df$predicted + 1)^2)
# lines(loess.smooth(resid_df$predicted, resid_df$res/(resid_df$predicted + 1)^2))
# abline(h = 0, lty = 2)


```


## Plotting parameter densities with priors
```{r, eval = TRUE}

spp_names <- emery %>% select(species, sppint) %>% 
  unique() %>% 
  arrange(sppint)


par <- c("shape1", "shape2", "stretch", "x_min", "x_max", "nu")
spp_par <- par
hier_par <- c("mu_shape1", "mu_shape2", "mu_stretch", "mu_min", "mu_max", "mu_nu")
param_letters <- c("shape1", "shape2", "stretch", "x_min", "x_max", "ν") %>% 
  as_tibble


plt_params <- function(p, den_rng, pr_mu, pr_sd, trunc, prior = T){
  datr <- posts[[spp_par[p]]] %>%
    as.data.frame() %>%
    set_colnames(spp_names$species) %>%
    gather(species, val)
  
  vis <- datr %>%
    ggplot() +
    geom_density(aes(x = val, color = species), lwd = 0.75, alpha = 0.25) +
    ggtitle(param_letters$value[p]) +
    theme_minimal() +
    xlim(den_rng[1], den_rng[2]) +
    theme(plot.title = element_text(hjust = 0.5))
  
  if(prior){
    vis <- vis + geom_area(stat = "function",
                           #fun = ifelse(missing(trunc), dnorm, dtruncnorm),
                           fun = dtruncnorm,
                           # args = ifelse(missing(trunc),
                           #               list(mean = pr_mu, sd = pr_sd),
                           #               list(mean = pr_mu, sd = pr_sd, a = trunc)
                           # ), 
                           args = list(mean = pr_mu, sd = pr_sd, a = trunc),
                           fill = "red",
                           alpha = 0.5,
                           colour="black",
                           xlim = den_rng) +
      geom_density( data = as_tibble(posts[[hier_par[p]]]), 
                    mapping = aes(x = value), 
                    fill = "dodgerblue",
                    alpha = 0.5)  
  }
  
  vis
}

cairo_pdf(filename = paste0("figures/B", 3, ".pdf"))
plt_params(p = 1, den_rng = c(2,6), pr_mu = 0, pr_sd = 1, trunc = 2)
dev.off()

cairo_pdf(filename = paste0("figures/B", 4, ".pdf"))
plt_params(p = 2, den_rng = c(2,6), pr_mu = 0, pr_sd = 1, trunc = 2)
dev.off()

cairo_pdf(filename = paste0("figures/B", 5, ".pdf"))
plt_params(p = 3, den_rng = c(0,3), pr_mu = 0, pr_sd = 1, trunc = 0)
dev.off()

cairo_pdf(filename = paste0("figures/B", 6, ".pdf"))
plt_params(p = 4, den_rng = c(-5,5), pr_mu = min(emery$treat), pr_sd = 1, trunc = -1000)
dev.off()

cairo_pdf(filename = paste0("figures/B", 7, ".pdf"))
plt_params(p = 5, den_rng = c(2,7), max(emery$treat), 1, trunc = -1000) 
dev.off()

cairo_pdf(filename = paste0("figures/B", 8, ".pdf"))
plt_params(p = 6, den_rng = c(1,25), 0, 1, trunc = -1000, prior = F)
dev.off()

# cairo_pdf(filename = paste0("figures/B", 9, ".pdf"))
# plt_params(p = 7, den_rng = c(-3,3), 0, 1) 
# dev.off()
# 
# cairo_pdf(filename = paste0("figures/B", 10, ".pdf"))
# plt_params(p = 8, den_rng = c(-3,3), 2, 1) #+ theme(legend.position="none")
# dev.off()

# xseq <- seq(0, 10, length.out = 100)
# out <- dtruncnorm(x = xseq, a = 2, mean = 0, sd = 1)
# plot(xseq, out)
```



## Correlation among parameters, within and among species
```{r, eval=FALSE}

theme_set(theme_minimal())

plot_pars <- function(df = draws, par1, par2, text1, text2){
  
  par_one <- enquo(par1)
  par_two <- enquo(par2)
  
  draws_sub <- df %>% select(species, !! par_one, !! par_two) %>%
    rename( par1 = !! par_one,
            par2 = !! par_two)
  
  grid_p <- draws_sub %>%
    ggplot(aes(par1, par2, colour = species)) +
    geom_point(alpha = 0.5) +
    xlab("") +
    ylab("") +
    facet_wrap(~species, nrow = 2) +
    theme(legend.position = "none")
  
  all_p <- draws_sub %>%
    ggplot(aes(par1, par2, colour = species)) +
    geom_point(alpha = 0.05) +
    xlab(text1) +
    ylab(text2)
  
  #grid_p #+ all_p + plot_layout(nrow = 2)
  all_p
  
}


plot_pars(par1 = shape2, par2 = x_max, text1 = "", text2 = "")


library(GGally)

# correl <- draws %>%
#   filter(draw %in% sample(1:ndraws, 500)) %>%
#   select(shape1, shape2, x_min, maxima, x_max, stretch, nu, species) %>%
#   as.data.frame() %>%
# ggscatmat(columns = 1:7, alpha = 0.05, color = "species") +
#   theme(legend.position = "blank") 

correl <- draws %>%
  filter(draw %in% sample(1:ndraws, 500)) %>%
  select(shape1, shape2, x_min, maxima, x_max, stretch, nu, species) %>%
  ggpairs(
    1:7, mapping = aes(color = species), 
  lower = list(continuous = wrap("points", alpha = 0.05, size = 1, shape = 1)), 
  #upper = list(continuous = wrap("points", alpha = 0.05, size = 1, shape = 1)),
  #upper = list(continuous = wrap("cor", size = 1, alignPercent = 1)),
  upper = "blank"
)

correl

mean_inflor <- emery %>% 
  group_by(species) %>%
  summarise(mean_inflor = mean(Inflor_biomass))

mean_depth <- wide_params %>%
  group_by(species) %>%
  summarise(mean_depth = mean(Mean),
            mean_stretch = mean(stretch_sc)) %>%
  full_join(., mean_inflor, by = "species")

cor(mean_depth$mean_stretch, mean_depth$mean_inflor)

cairo_pdf("figures/lm_depth.pdf")
mean_depth %>%
  ggplot(aes(mean_inflor, mean_depth)) +
  geom_point() +
  geom_smooth(method = "lm")
dev.off()


lm(mean_depth ~ mean_inflor, data = mean_depth) %>%
  summary %>%
  coef()

```

